Jug: Software for Reproducible Computation

### 2011-12-08 paper.tex
MIN Add link to previous paper's archives
MIN Update download count
A few downloads since last release

Jug has been available in the Python Package Index\footnote{The Python Package
Index, PyPI, is accessible at \url{http://pypi.python.org}.} since May~2009
and has been downloaded over 6000~times (some of these downloads may, of
course, represent upgrades, and users which downloaded it from some other
source will not be counted).% FIXME: Check download number. At 5713 8/31/2011

@@

In the last few years, I have not undertaken any computational research project
without the use of jug to manage my computations. The tool has become an
indispensible part of my toolkit.

>>>>

Jug has been available in the Python Package Index\footnote{The Python Package
Index, PyPI, is accessible at \url{http://pypi.python.org}.} since May~2009
and has been downloaded over 8000~times (some of these downloads may, of
course, represent upgrades, and users which downloaded it from some other
source will not be counted).% FIXME: Check download number. At 8112 12/8/2011

@@

In the last few years, I have not undertaken any computational research project
without the use of jug to manage my computations. Additionally, I (and my
co-authors) have made the resulting results directories available\footnote{See
the links at
\url{http://murphylab.cbi.cmu.edu/software/software_from_papers.html}}. The
tool has become an indispensible part of my toolkit.
